Synthesizing Symmetric Lenses

### 2018-07-05 papers/SymmetricLenses/main.tex
fix theorem statement

\subsection{Lens Costs}
Our cost metric is based on the expected amount of information required to
recover a string in one data format from the other. We use the function
$\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ to calculate the expected amount
of information required to recover a string in $\Regex$ from a string in
$\RegexAlt$, synchronized by $\Lens$. We use the function
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ to calculate the expected amount
of information required to recover a string in $\RegexAlt$ from a string in
$\Regex$, synchronized by $\Lens$.
\begin{center}
  \begin{tabular}{rcl}
    $\REntropyOf{\Regex \Given \IdentityLensOf{\Regex}, \Regex}$
    & =
    & 0\\

    $\REntropyOf{\Regex \Given \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, \RegexAlt}$
    & =
    & \EntropyOf{\RegexAlt}\\

    $\REntropyOf{\PRegexStar{\Regex}{\Probability} \Given \IterateLensOf{\Lens}^, \PRegexStar{\RegexAlt}{\ProbabilityAlt}}$
    & =
    & $\frac{\Probability}{1-\Probability}(\REntropyOf{\Regex \Given \Lens, \RegexAlt})$\\

    $\REntropyOf{\Regex_1 \Concat \Regex_2 \Given \ConcatLensOf{\Lens_1}{\Lens_2}, \RegexAlt_1 \Concat \RegexAlt_2}$
    & =
    & $\REntropyOf{\Regex_1 \Given \Lens_1^\leftarrow, \RegexAlt_1} + \REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\REntropyOf{\Regex_1 \Concat \Regex_2 \Given \SwapLensOf{\Lens_1}{\Lens_2}, \RegexAlt_2 \Concat \RegexAlt_1}$
    & =
    & $\REntropyOf{\Regex_1 \Given \Lens_1^\leftarrow, \RegexAlt_1} + \REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2}$\\

    $\REntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\Probability*(\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1} ) + (1-\Probability)*(\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2})$\\

    $\REntropyOf{\PRegexOr{\Regex_1}{\Regex_2}{\Probability} \Given \MergeROf{\Lens_1}{\Lens_2}, \RegexAlt}$
    & =
    & $\Probability*(\REntropyOf{\Regex \Given \Lens_1, \RegexAlt_1}) + (1-\Probability)*(\REntropyOf{\Regex \Given \Lens_2, \RegexAlt_2})$\\

    $\REntropyOf{\Regex \Given \MergeLOf{\Lens_1}{\Lens_2}, \PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}}$
    & =
    & $\ProbabilityAlt*(\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt} - \Log_2(\ProbabilityAlt)) + $\\
    &
    & $(1-\ProbabilityAlt)*(\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt} - \Log_2(1 - \ProbabilityAlt))$\\

    $\REntropyOf{\RegexAlt \Given \InvertOf{\Lens}, \Regex}$
    & =
    & $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\RegexAlt \Given \Lens, \Regex}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, they should be
  included.}

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\LEntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem}

@@

\begin{theorem*}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \item $\LEntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \end{enumerate}
\end{theorem*}
\begin{proof}
Given $s \in S$, let $V_{\ell}(s) = \{t \in \mathcal{L}(T) \; | \; \ell.\PutROf{s}{t} = t\}$. We want to show that
$$\sum_{s \in \mathcal{L}(S)}P_{\mathcal{L}(S)}(s)H(V_{\ell}(s)) = \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)$$
We proceed by induction over $\ell$. 
\begin{enumerate}
\item
($\ell = \IdentityLensOf{S}$)

>>>>

\subsection{Lens Costs}
Our cost metric is based on the expected amount of information required to
recover a string in one data format from the other. We use the function
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ to calculate the expected amount
of information required to recover a string in $\RegexAlt$ from a string in
$\Regex$, synchronized by $\Lens$. We use the function $\LEntropyOf{\Regex
  \Given \Lens, \RegexAlt}$ to calculate the expected amount of information
required to recover a string in $\Regex$ from a string in $\RegexAlt$,
synchronized by $\Lens$.
\begin{center}
  \begin{tabular}{rcl}
    $\REntropyOf{\RegexAlt \Given \IdentityLensOf{\RegexAlt}, \RegexAlt}$
    & =
    & 0\\

    $\REntropyOf{\RegexAlt \Given \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, \Regex}$
    & =
    & \EntropyOf{\RegexAlt}\\

    $\REntropyOf{\PRegexStar{\RegexAlt}{\ProbabilityAlt} \Given \IterateLensOf{\Lens}, \PRegexStar{\Regex}{\Probability}}$
    & =
    & $\frac{\Probability}{1-\Probability}(\REntropyOf{\RegexAlt \Given \Lens, \Regex})$\\

    $\REntropyOf{\RegexAlt_1 \Concat \RegexAlt_2 \Given \ConcatLensOf{\Lens_1}{\Lens_2}, \Regex_1 \Concat \Regex_2}$
    & =
    & $\REntropyOf{\RegexAlt_1 \Given \Lens_1, \Regex_1} + \REntropyOf{\RegexAlt_2 \Given \Lens_2, \Regex_2}$\\

    $\REntropyOf{\RegexAlt_2 \Concat \RegexAlt_1 \Given \SwapLensOf{\Lens_1}{\Lens_2}, \Regex_1 \Concat \Regex_2}$
    & =
    & $\REntropyOf{\RegexAlt_2 \Given \Lens_1, \Regex_2} + \REntropyOf{\RegexAlt_1 \Given \Lens_1, \Regex_1}$\\

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \OrLensOf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability*(\REntropyOf{\Regex_1 \Given \Lens_1, \RegexAlt_1} ) + (1-\Probability)*(\REntropyOf{\Regex_2 \Given \Lens_2, \RegexAlt_2})$\\

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \MergeLOf{\Lens_1}{\Lens_2}, \Regex}$
    & =
    & $\ProbabilityAlt*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}) + (1-\ProbabilityAlt)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2})$\\

    $\REntropyOf{\RegexAlt \Given \MergeROf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1} - \Log_2(\Probability)) + $\\
    &
    & $(1-\Probability)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2} - \Log_2(1 - \Probability))$\\

    $\REntropyOf{\Regex \Given \InvertOf{\Lens}, \RegexAlt}$
    & =
    & $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, they should be
  included.}

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \item $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \end{enumerate}
\end{theorem}

@@

\begin{theorem*}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \item $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \end{enumerate}
\end{theorem*}
\begin{proof}
Given $s \in S$, let $V_{\ell}(s) = \{t \in \mathcal{L}(T) \; | \; \ell.\PutROf{s}{t} = t\}$. We want to show that
$$\sum_{s \in \mathcal{L}(S)}P_{\mathcal{L}(S)}(s)H(V_{\ell}(s)) = \mathbb{H}^{\rightarrow}(S \; | \; \ell, T)$$
We proceed by induction over $\ell$. 
\begin{enumerate}
\item
($\ell = \IdentityLensOf{S}$)
